% Related Work
\section{Related Work}
\label{RW}

%Introduce the representative existing algorithms and their weakness.

%Cite
%Algorithms:

%Deterministic:
%BlindDate 					#wang2015blinddate		*
%Disco 						#dutta2008practical
%Hello 						#sun2014hello
%Searchlight 					#bakht2012searchlight
%Talk More Listen Less 			#qiu2016talk			*
%Todis\&Hedis 					#chen2015heterogeneous
%U-Connect  					#kandhalu2010u

%probabilistic:
%Birthday 					#mcglynn2001birthday
%ALOHA-like09 				#vasudevan2009neighbor
%ALOHA-like11 	 			#you2011aloha
%PND 						#song2014probabilistic

%others
%Normal Distribution 			#wang2013gaussian
%Beacon&package 				#mcglynn2001birthday
%RSSI						#daiya2011experimental
%Chinese Remainder Theorem		#ding1996chinese



Existing neighbor discovery algorithms can be classified into two
categories: deterministic and probabilistic.

Deterministic algorithms adopt certain mathematical tools to ensure
discovery between every two neighbors. The first tool is the quorum
system~\cite{luk1997two}: for any two intersected
quorums, two neighboring nodes could choose any quorum in the system to
design the discovery schedule. Hedis~\cite{chen2015heterogeneous} is a
typical one. Another important tool is co-primality where two co-prime
numbers are chosen by the neighbors to design the discovery schedule,
and they can discover each other within a bounded latency by the Chinese
Remainder Theorem~\cite{ding1996chinese}. Some representative algorithms
are Disco~\cite{dutta2008practical}, U-Connect~\cite{kandhalu2010u}, and
Todis~\cite{chen2015heterogeneous}. These algorithms have the obvious
advantage that they can guarantee fast discovery for two nodes within a
bounded latency.

However, there are weaknesses in these deterministic algorithms when they are applied to large-scale networks.
Hedis \cite{chen2015heterogeneous} only assumes that only when two nodes
turn on the radio at the same time can they they then find each other.
However, in reality, neighbors play asymmetric roles and one is
transmitting while the other one is receiving.
U-Connect~\cite{kandhalu2010u} considers the transmitting and receiving roles.
Nevertheless, different from the two-node scenario, collisions will happen when many nodes are transmitting simultaneously. 
Some deterministic algorithms propose a beacon-based transmission protocol.
For example, Disco~\cite{dutta2008practical} assumes that a node has a
capability to send a beacon (comprising one or a few bits) at both the beginning
and the end of an active time slot, and the assumption is adopted in 
SearchLight~\cite{bakht2012searchlight}, Hello~\cite{sun2014hello}, and
Nihao~\cite{qiu2016talk}.
Under this assumption, the listening time slot is much larger than the
transmitting time slot and collisions can thus be avoided.
Nevertheless, this mechanism makes a complete slot 
40 times larger than that of U-Connect~\cite{kandhalu2010u} and thus cannot
promise a reasonable discovery latency.
%Under the assumption, these algorithms could guarantee discovery
%between two nodes within an ideal latency. But sending a beacon may not
%work well in a large-scale network since a node needs to distinguish
%its neighbors by the received messages, which implies a transmitted
%package should contain the sender node's
%information\cite{zhou2004impact}.

Another category is probabilistic algorithms \cite{mcglynn2001birthday,
vasudevan2009neighbor,you2011aloha,song2014probabilistic} which utilize
probability techniques to inject randomness into the discovery process. 
Birthday protocol \cite{mcglynn2001birthday} is one of the earliest algorithms that works on the birthday
paradox, i.e. the probability that two people have the same
birthday exceeds $\frac{1}{2}$ among $23$ people. Following that,
smarter probabilistic algorithms are proposed, such as an Aloha-like
algorithm \cite{vasudevan2009neighbor, you2011aloha}, PND
\cite{song2014probabilistic}. Particularly, the Aloha-like algorithm
\cite{vasudevan2009neighbor} does not consider energy consumption,
which was later extended to an energy-restricted network by
\cite{you2011aloha}.

Unlike deterministic algorithms,
probabilistic algorithms show significant strength for a network consisting of multiple nodes.
However, probabilistic algorithms can only give an expectation for the
discovery latency and cannot guarantee a good latency bound.
In addition, most of the existing algorithms assume the network is a clique, which implies any two nodes are neighbors. 
This assumption can hardly match the situation of a large-scale network.
%due to the limited communication range of a node.
Some work uses the received signal strength to decide how far a node
can transmit~\cite{daiya2011experimental}, and in the protocol model,
this is simplified to be that two nodes can communicate if their distance is no
larger than a threshold.


%We implement some probabilistic protocols for a large-scale network and the results show that they have a poor performance (see Section \ref{Evaluation}).
%To the best of our knowledge, neither deterministic nor probabilistic algorithms have good performance when they are adopted in an energy-restricted large-scale network.
